Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-09 article_springer/article_springer.Rmd
remove cross-reference

To test our inference method via stability plots, we have simulated 
independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
analytical values available for $\beta$ and $\sigma_0$, a distribution for 
$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
then due to the stability property we have the *equality* of distribution
$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
for $b(n) = n^{1/\beta}$. 
Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
calculation [see e.g. the vignette on parametrisation in @MittagLeffleR]
show that $D$ must have the stable distribution 
$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
implemented in the R package `stabledist` by @stabledist.

>>>>

To test our inference method via stability plots, we have simulated 
independent waiting time and magnitude pairs $(W_k, J_k)$ for three different
situations: stable waiting times, Pareto waitings times and Exponential waiting 
times. In order to have exact 
analytical values available for $\beta$ and $\sigma_0$, a distribution for 
$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
then due to the stability property we have the *equality* of distribution
$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
for $b(n) = n^{1/\beta}$. 
Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
calculation [see e.g. the vignette on parametrisation in @MittagLeffleR]
show that $D$ must have the stable distribution 
$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
implemented in the R package `stabledist` by @stabledist.
